---
title: "Optogenetics Joystick Screen"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    keep_md: FALSE
---
<style type="text/css">
  body .main-container {
    max-width: 1800px !important;
  }
  h1.title {
  font-size: 38px;
  color: DarkRed;
  text-align: center;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<center>Rendered on `r format(Sys.time(), '%d %B %Y')`</center>

# PI profile of all groups

## Performance Index bar plot with SEM

```{r PIbar, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.align = "center", fig.height = 140, fig.width = 20, comment=NA, results='asis'}
sequencecolors = c("lightyellow","lightyellow","orange","orange","lightyellow","lightyellow","orange","orange","lightyellow","lightyellow")

PIplots <- list()
for(x in 1:length(groupedPIs))
  {
    PIprofile <- groupedPIs[[x]] #get PIs

    # plot graph
     PIplots[[x]] <- ggplot(melt(na.omit(PIprofile)), aes(x=variable, y=value)) + 
              geom_hline(yintercept = 0, colour = "#887000", size = 1.2) +
              stat_summary(geom = "bar", fun = mean, position = "dodge", fill=sequencecolors, colour="black", width=1) +
              stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge", width=0, size=2) +
              ggtitle(paste(names(groupedPIs)[x], ", N=",nrow(na.omit(groupedPIs[[x]])))) +
              scale_y_continuous(breaks = seq(-1, 1, .2)) +
              theme_light(base_size = 16) + 
              theme(panel.grid.major.x = element_blank(),panel.grid.minor = element_blank(), panel.border = element_rect(size = 0.5, linetype = "solid", colour = "black", fill=NA)) +
              theme(axis.text.y = element_text(size=18))+ 
              ylab("PI [rel. units]") + 
              xlab("Experiment Sequence")
  }
grid.arrange(grobs = PIplots, nrow=no_of_screens)
```

## Performance Index box&dotplot without notches:

```{r BoxNoNotch, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.align = "center", fig.height = 140, fig.width = 20, comment=NA, results='asis'}

for(x in 1:length(groupedPIs))
  {
    PIprofile <- groupedPIs[[x]] #get PIs

    #plot graph
    PIplots[[x]] <- ggplot(melt(na.omit(PIprofile)), aes(x=variable, y=value)) +
              geom_hline(yintercept = 0, colour = "#887000", size = 1.2) +
              geom_boxplot(fill = sequencecolors, notch = FALSE, outlier.color=NA, width=0.8, size=0.6) +
              geom_jitter(data = melt(na.omit(PIprofile)), aes(variable, value), position=position_jitter(0.3), shape=21, size=3, fill="lightgrey", alpha=0.5) +
              ggtitle(paste(names(groupedPIs)[x], ", N=",nrow(na.omit(groupedPIs[[x]])))) +
              scale_y_continuous(breaks = seq(-1, 1, .4)) +
              theme_light(base_size = 16) + 
              theme(panel.grid.minor = element_blank(), panel.grid.major.x = element_blank() ,panel.border = element_rect(size = 0.5, linetype = "solid", colour = "black", fill=NA)) +
              theme(axis.text.y = element_text(size=18))+ 
              ylab("PI [rel. units]")+ 
              xlab("Experiment Sequence")
    }        
grid.arrange(grobs = PIplots, nrow=no_of_screens)
```

# Group comparisons

```{r PIcomps, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, comment=NA, results='asis'}
#####some computations to the PI dataframes

for(x in 1:length(groupedPIs))
{
  groupedPIs[[x]]$group <- names(groupedPIs)[x] #1 add group names as variable
  groupedPIs[[x]]$ave_tr <- rowMeans(subset(groupedPIs[[x]], select = c(training1,training2,training3,training4))) #2 average all training values
  groupedPIs[[x]]$ave_pt <- rowMeans(subset(groupedPIs[[x]], select = c(pretest1,pretest2))) #2a average pretest values
  groupedPIs[[x]]$te_pt <- groupedPIs[[x]]$test3-groupedPIs[[x]]$ave_pt #3 subtract pretest from final test
  groupedPIs[[x]]$ltr_pt <- groupedPIs[[x]]$training4-groupedPIs[[x]]$ave_pt #4 subtract pretest from last training
  groupedPIs[[x]]$atr_pt <- groupedPIs[[x]]$ave_tr-groupedPIs[[x]]$ave_pt #5 subtract pretest from averaged training
}

######Generate melted, long form dataframe with all the interesting single parameters
PIs<-as.data.frame(matrix(ncol=7,nrow=sum(sapply(groupedPIs, nrow))))
colnames(PIs)=c("group","last_training","test","average_training","testMpretest","lastTrainingMpretest","averTrainingMpretest") #dataframe with a grouping variable first
PIs$group<-unlist(rbind(lapply(groupedPIs, "[", , "group")))
PIs$last_training<-unlist(rbind(lapply(groupedPIs, "[", , "training4")))
PIs$test<-unlist(rbind(lapply(groupedPIs, "[", , "test3")))
PIs$average_training<-unlist(rbind(lapply(groupedPIs, "[", , "ave_tr")))
PIs$testMpretest<-unlist(rbind(lapply(groupedPIs, "[", , "te_pt")))
PIs$lastTrainingMpretest<-unlist(rbind(lapply(groupedPIs, "[", , "ltr_pt")))
PIs$averTrainingMpretest<-unlist(rbind(lapply(groupedPIs, "[", , "atr_pt")))

samplesizes=as.vector(table(PIs$group))
boxes<-c(1:no_of_screens)
boxcolors=c("blue1","blue3","blue4","forestgreen","green2","green3","deeppink1","deeppink3","deeppink4","yellow1","yellow2","yellow3","yellow4","olivedrab1","olivedrab2","olivedrab4","yellow","orange1","orange2","orange3","orange4","red1","red2","red3","white","azure2","springgreen4") #set the colors for the plots

```

## Last training PI

```{r LastTrPI, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.align = "center", fig.height = 8, fig.width = 16, comment=NA, results='asis'}

ggplot(PIs, aes(group, last_training)) +
    geom_hline(yintercept = 0, colour = "#887000", size = 1.2) +
    geom_boxplot(fill = boxcolors, notch = FALSE, outlier.color=NA, width=0.8, size=0.6) +
    geom_jitter(data=PIs, aes(group, last_training), position=position_jitter(0.3), shape=21, size=3, alpha=0.5, fill="grey") +
    scale_y_continuous(breaks = seq(-1, 1, .2)) +
    theme_light(base_size = 16) + theme(panel.grid.minor = element_blank(), panel.grid.major.x = element_blank() ,panel.border = element_rect(size = 0.5, linetype = "solid", colour = "black", fill=NA)) +
    theme(axis.text.y = element_text(size=18))+ ylab("PI of last training period [rel. units]")+ xlab("Groups")+ theme(aspect.ratio=0.5)+
    theme(axis.text.x = element_text(angle = 60, hjust = 1))+
    samplesizes.annotate(boxes, samplesizes)
```

## Last training PI minus pretest

```{r LastTrMpt, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.align = "center", fig.height = 8, fig.width = 16, comment=NA, results='asis'}

ggplot(PIs, aes(group, lastTrainingMpretest)) +
    geom_hline(yintercept = 0, colour = "#887000", size = 1.2) +
    geom_boxplot(fill = boxcolors, notch = FALSE, outlier.color=NA, width=0.8, size=0.6) +
    geom_jitter(data=PIs, aes(group, lastTrainingMpretest), position=position_jitter(0.3), shape=21, size=3, alpha=0.5, fill="grey") +
    scale_y_continuous(breaks = seq(-1, 1, .2)) +
    theme_light(base_size = 16) + theme(panel.grid.minor = element_blank(), panel.grid.major.x = element_blank() ,panel.border = element_rect(size = 0.5, linetype = "solid", colour = "black", fill=NA)) +
    theme(axis.text.y = element_text(size=18))+ ylab("PI of last training (-PT) [rel. units]")+ xlab("Groups")+ theme(aspect.ratio=0.5)+
    theme(axis.text.x = element_text(angle = 60, hjust = 1))+
    samplesizes.annotate(boxes, samplesizes)
```

## Averaged training PIs

```{r AveTr, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.align = "center", fig.height = 8, fig.width = 16, comment=NA, results='asis'}

ggplot(PIs, aes(group, average_training)) +
    geom_hline(yintercept = 0, colour = "#887000", size = 1.2) +
    geom_boxplot(fill = boxcolors, notch = FALSE, outlier.color=NA, width=0.8, size=0.6) +
    geom_jitter(data=PIs, aes(group, average_training), position=position_jitter(0.3), shape=21, size=3, alpha=0.5, fill="grey") +
    scale_y_continuous(breaks = seq(-1, 1, .2)) +
    theme_light(base_size = 16) + theme(panel.grid.minor = element_blank(), panel.grid.major.x = element_blank() ,panel.border = element_rect(size = 0.5, linetype = "solid", colour = "black", fill=NA)) +
    theme(axis.text.y = element_text(size=18))+ ylab("Average training PI [rel. units]")+ xlab("Groups")+ theme(aspect.ratio=0.5)+
    theme(axis.text.x = element_text(angle = 60, hjust = 1))+
    samplesizes.annotate(boxes, samplesizes)
```

## Averaged training PIs minus pretest

```{r AveTrMpt, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.align = "center", fig.height = 8, fig.width = 16, comment=NA, results='asis'}

ggplot(PIs, aes(group, averTrainingMpretest)) +
    geom_hline(yintercept = 0, colour = "#887000", size = 1.2) +
    geom_boxplot(fill = boxcolors, notch = FALSE, outlier.color=NA, width=0.8, size=0.6) +
    geom_jitter(data=PIs, aes(group, averTrainingMpretest), position=position_jitter(0.3), shape=21, size=3, alpha=0.5, fill="grey") +
    scale_y_continuous(breaks = seq(-1, 1, .2)) +
    theme_light(base_size = 16) + theme(panel.grid.minor = element_blank(), panel.grid.major.x = element_blank() ,panel.border = element_rect(size = 0.5, linetype = "solid", colour = "black", fill=NA)) +
    theme(axis.text.y = element_text(size=18))+ ylab("Average training PI (-PT) [rel. units]")+ xlab("Groups")+ theme(aspect.ratio=0.5)+
    theme(axis.text.x = element_text(angle = 60, hjust = 1))+
    samplesizes.annotate(boxes, samplesizes)
```

## Test PI

```{r testPI, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.align = "center", fig.height = 8, fig.width = 16, comment=NA, results='asis'}

ggplot(PIs, aes(group, test)) +
    geom_hline(yintercept = 0, colour = "#887000", size = 1.2) +
    geom_boxplot(fill = boxcolors, notch = FALSE, outlier.color=NA, width=0.8, size=0.6) +
    geom_jitter(data=PIs, aes(group, test), position=position_jitter(0.3), shape=21, size=3, alpha=0.5, fill="grey") +
    scale_y_continuous(breaks = seq(-1, 1, .2)) +
    theme_light(base_size = 16) + theme(panel.grid.minor = element_blank(), panel.grid.major.x = element_blank() ,panel.border = element_rect(size = 0.5, linetype = "solid", colour = "black", fill=NA)) +
    theme(axis.text.y = element_text(size=18))+ ylab("Test PI [rel. units]")+ xlab("Groups")+ theme(aspect.ratio=0.5)+
    theme(axis.text.x = element_text(angle = 60, hjust = 1))+
    samplesizes.annotate(boxes, samplesizes)
```

## Test PI minus pretest

```{r testPIMpt, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.align = "center", fig.height = 8, fig.width = 16, comment=NA, results='asis'}

ggplot(PIs, aes(group, testMpretest)) +
    geom_hline(yintercept = 0, colour = "#887000", size = 1.2) +
    geom_boxplot(fill = boxcolors, notch = FALSE, outlier.color=NA, width=0.8, size=0.6) +
    geom_jitter(data=PIs, aes(group, testMpretest), position=position_jitter(0.3), shape=21, size=3, alpha=0.5, fill="grey") +
    scale_y_continuous(breaks = seq(-1, 1, .2)) +
    theme_light(base_size = 16) + theme(panel.grid.minor = element_blank(), panel.grid.major.x = element_blank() ,panel.border = element_rect(size = 0.5, linetype = "solid", colour = "black", fill=NA)) +
    theme(axis.text.y = element_text(size=18))+ ylab("Test PI (-PT) [rel. units]")+ xlab("Groups")+ theme(aspect.ratio=0.5)+
    theme(axis.text.x = element_text(angle = 60, hjust = 1))+
    samplesizes.annotate(boxes, samplesizes)
```